A recipe for extremely reproducible enrichment analysis

### 2023-04-13 manuscript.Rmd
Update manuscript.Rmd

| --- | --- | --- | --- | --- | --- |

@@

| 6. | PMC6444048	| The text under “Pathway analysis of SUVmax related genes” And Table 2 |	1. Terms are the same but gene counts have been different. The DAVID results are somewhat reproducible. 2. No |	1. Gene counts in the terms significantly enriched in the “process of cell division” and “nucleoplasm” has changed. 
2. Only cell cycle is highly enriched in the replicated results, the claims of metabolic pathways and hypoxia signalling (through GSEA analysis) to be enriched are not accurate. The results claimed are somewhat similar. All the processes have different FDR values. | 3 |

@@

| 8. | PMC6535219 |	Figure 2 | 1. Somewhat similar. 2. There were many top significant terms that were not mentioned.	Narrowing/Filtering the given gene list is a required step that could have been mentioned. Many terms were not so significant anymore. There were new terms that are of top positions after replication. | 1 |
| 9. | PMC6539328 |	Figure 1A |	1. Mostly not. 2. Yes, many	The significant pathways stated in the paper are not showing up once replicated. There is no clarity of the up-regulated genes used for GO and KEGG analysis. Only 21 upregulated genes are listed whereas the paper states 4831. Also, why are only upregulated genes are being used? | 1 |

>>>>

| --- | --- | ----- | ----- | ----- | --- |

@@

| 6. | PMC6444048	| The text under “Pathway analysis of SUVmax related genes” And Table 2 |	1. Terms are the same but gene counts have been different. The DAVID results are somewhat reproducible. 2. No |	1. Gene counts in the terms significantly enriched in the “process of cell division” and “nucleoplasm” has changed. 2. Only cell cycle is highly enriched in the replicated results, the claims of metabolic pathways and hypoxia signalling (through GSEA analysis) to be enriched are not accurate. The results claimed are somewhat similar. All the processes have different FDR values. | 3 |

@@

| 8. | PMC6535219 |	Figure 2 | 1. Somewhat similar. 2. There were many top significant terms that were not mentioned. |	Narrowing/Filtering the given gene list is a required step that could have been mentioned. Many terms were not so significant anymore. There were new terms that are of top positions after replication. | 1 |
| 9. | PMC6539328 |	Figure 1A |	1. Mostly not. 2. Yes, many | The significant pathways stated in the paper are not showing up once replicated. There is no clarity of the up-regulated genes used for GO and KEGG analysis. Only 21 upregulated genes are listed whereas the paper states 4831. Also, why are only upregulated genes are being used? | 1 |
